---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rabinoffmmmr

<!-- badges: start -->
<!-- badges: end -->

The goal of rabinoffmmmr is to provide an interface for building and employing media mix models that more closely resembles building and employing standard statistical and machine learning models. Model parameters will be stored in an initial model spec object of class `mmmr`, which then can be used with `fit`, `predict`, and `coef`. Plotting and reporting functions will be added.

## Installation

You can install the development version of rabinoffmmmr like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rabinoffmmmr)
## basic example code
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:
